\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-02-26 tex/paper.tex
Added a bit of introduction

%}}}
\section{Introduction}
Developing large projects containing static content usually involves using a Content Distribution
Network to be able to scale to a larger user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines ways of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed to make the underlying theory work in practice.

@@

\fix Clarify problem definition and research questions
\newpage
\section{Background}
This section gives the reader some background of the company where the thesis was written and
implementation was made. It also gives some brief explanation of the core concepts which are 
exerted throughout this work.

@@

\fix Polish and extend

>>>>

%}}}
\section{Introduction}
Developing large projects containing static content usually involves using a Content Distribution
Network to be able to scale to a larger user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines a way of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed using the Copy-on-Write principle to improve scalability and make
it a lighter operation to take snapshots.

@@

\newpage
\section{Background}
This section gives the reader some background of the company where the thesis was written and
implementation was made. It also gives some brief explanation of the core concepts which are 
exerted throughout this work.

@@
